\textbf{systemfit}\\ Simultaneous Equation Systems in R

### 2008-09-25 paper/trunk/Slides/systemfit_slides.tex
moved /paper/branches/useR2006/Slides to /paper/trunk/Slides/
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@975 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\title[systemfit]{
   \textbf{systemfit}\\ Simultaneous Equation Systems in R}
\author{Arne Henningsen (University of Kiel, Germany)\\[0.4em]
   Jeff D.\ Hamann (Forest Informatics, Inc., Corvallis, USA)}
\date{Vienna, June 16, 2006}

@@

% ----------------- General Plans for the Future ----------------------------
\subsection{General}
\frame{
   \frametitle{Plans for the Future}
\begin{itemize}
\setlength{\itemsep}{0.75em}
\item estimation with unbalanced data sets
\item estimation methods: LIML, FIML,  and GMM
\item fitting equation systems with serially correlated and
heteroscedastic disturbances
\item spatial econometric methods
\item improving the function \texttt{nlsystemfit}
to estimate systems of non-linear equations
\item \ldots
\end{itemize}
}
\note{
\begin{itemize}
\item Although systemfit has many features and produces
   reliable results,
   there are still many things that can be added to the package.
\item For instance, we plan to allow for an estimation with
   unbalanced data sets -- these are datasets with unequal numbers
   of observations for each equation.
\item Then we would like to add the estimation methods
   °Limited Information Maximum Likelihood°,
   °Full Information Maximum Likelihood°, and
   °Generalized Method of Moments°.
\item Furthermore, we plan to add estimation procedures
   that account for serially correlated and heteroscedastic disturbances
   as well as for spatial data.
\item Finally, we would like to improve the function \texttt{nlsystemfit}
   to estimate systems of non-linear equations.
\item And there are of other things that can be improved.
\item If you are interested,
   you are invited to help us improving systemfit.
\end{itemize}
}

@@

\frame{
   \frametitle{Arguments}
Reducing arguments?\\[3mm]
\begin{minipage}{0.25\textwidth}
\begin{itemize}
\item method
\item eqns
\item inst
\item data
\end{itemize}
\end{minipage}
\begin{minipage}{0.55\textwidth}
\begin{itemize}
\item R.restr
\item q.restr
\item TX
\item \textbf{control} (like in \texttt{optim})
\end{itemize}
\end{minipage}\\[5mm]
However: This would break existing code!
}
\note{
\begin{itemize}
\item Therefore, we are consider whether we should reduce the number
   of arguments.
\item All arguments that are generally not used by unadvanced,
   could be subsumed into a list of control parameters
   like in the function °optim°.
\item However: This would break existing code!
\item I would like to know what you think about this issue.
\item Do you think we should reduce the arguments
   or keep all arguments as they are?
\item Or do you have a better solution to make the function more concise?
\end{itemize}
}

>>>>

\title[systemfit]{
   \textbf{systemfit}\\ Simultaneous Equation Systems in R}
\author[Arne Henningsen and Jeff D.\ Hamann]{
   Arne Henningsen (University of Kiel, Germany)\\[0.4em]
   Jeff D.\ Hamann (Forest Informatics, Inc., Corvallis, USA)}
\date{useR!, Vienna, June 16, 2006}

@@

% ----------------- General Plans for the Future ----------------------------
\subsection{General}
\frame{
   \frametitle{Plans for the Future}
\begin{itemize}
\setlength{\itemsep}{0.75em}
\item estimation with unbalanced data sets
\item estimation methods: LIML, FIML,  and GMM
\item fitting equation systems with serially correlated and
heteroscedastic disturbances
\item spatial econometric methods
\item simplify specification of parameter restrictions
\item improving the function \texttt{nlsystemfit}
to estimate systems of non-linear equations
\item \ldots
\end{itemize}
}
\note{
\begin{itemize}
\item Although systemfit has many features and produces
   reliable results,
   there are still many things that can be added to the package.
\item For instance, we plan to allow for an estimation with
   unbalanced data sets -- these are datasets with unequal numbers
   of observations for each equation.
\item Then we would like to add the estimation methods
   °Limited Information Maximum Likelihood°,
   °Full Information Maximum Likelihood°, and
   °Generalized Method of Moments°.
\item Furthermore, we plan to add estimation procedures
   that account for serially correlated and heteroscedastic disturbances
   as well as for spatial data.
\item And we would like to simplify the specification of parameter
   restrictions.
\item Finally, we would like to improve the function \texttt{nlsystemfit}
   to estimate systems of non-linear equations.
\item And there are of other things that can be improved.
\item If you are interested,
   you are invited to help us improving systemfit.
\end{itemize}
}

@@

\frame{
   \frametitle{Arguments}
Reducing arguments?\\[3mm]
\begin{minipage}{0.25\textwidth}
\begin{itemize}
\item method
\item eqns
\item inst
\item data
\end{itemize}
\end{minipage}
\begin{minipage}{0.55\textwidth}
\begin{itemize}
\item R.restr
\item q.restr
\item TX
\item \textbf{control} (like in \texttt{optim})
\end{itemize}
\end{minipage}\\[5mm]
However: This would break existing code!
}
\note{
\begin{itemize}
\item Therefore, we consider whether we should reduce the number
   of arguments.
\item All arguments that are generally not used by unadvanced users,
   could be subsumed into a list of control parameters
   like in the function °optim°.
\item However: This would break existing code!
\item I would like to know what you think about this issue.
\item Do you think we should reduce the arguments
   or keep all arguments as they are?
\item Or do you have a better solution to make the function more concise?
\end{itemize}
}
